Calculating life expectancy and exploring missingness

### 2016-10-26 Code/1_Explore_Data_v2.Rmd
more cod decomp changes

```{r load_libs, echo=F, warning=F, message=F}
library(plyr)
library(dplyr)
library(ggplot2)
library(tidyr)
```

@@

Add the life expectancy at birth to the data file

@@

>>>>

```{r load_libs, echo=F, warning=F, message=F}
library(plyr)
library(dplyr)
library(ggplot2)
library(tidyr)
source("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Code/life_expectancy_functions.R")
```

@@

Add the life expectancy at birth to the data file:

@@

i <- 1
white.index <- which(non.zero.stratums == paired.ids[i, "StateYearRaceSexWhite"])
black.index <- which(non.zero.stratums == paired.ids[i, "StateYearRaceSexBlack"])

    ct.white <- subset(dat.clean, StateYearRaceSex == paired.ids[i, "StateYearRaceSexWhite"]) %>% 
                ungroup() %>%
                select(Age2, COD2, cod_prop_death5) %>%
                rename(prop.white = cod_prop_death5)

    ct.black <- subset(dat.clean, StateYearRaceSex == paired.ids[i, "StateYearRaceSexBlack"]) %>% 
                ungroup() %>%
                select(Age2, COD2, cod_prop_death5) %>%
                rename(prop.black = cod_prop_death5)
    ct.both <- merge(ct.white, ct.black, by = c("Age2", "COD2"))
